---
title: "HW 3"
author: "Weiren Wang"
date: "February 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### 3.8.1.1
```{r pckgs, warning= FALSE, message= FALSE}
library(ggplot2)
```

#Section 3.8.1
### 1. 
```{r 3.8.1.1}
ggplot(data = mpg, mapping = aes(x= cty, y= hwy))+
  geom_point(position = "jitter")
```
The values of cty and hwy are rounded so the points appear on a grid and many points overlap each other, which is known as overplotting. This problem can be avoided by setting the position adjustment to "jitter" which adds a small amount of random noise to each point. This spreads the points out because no two points are likely to receive the same amount of random noise. 
### 2. 
width and height to geom_jitter() control the amount of jittering. 

### 3. 
```{r 3.8.1.3}
ggplot(data = mpg, mapping = aes(x = cty, y= hwy))+
  geom_jitter()
ggplot(data = mpg, mapping = aes(x = cty, y= hwy))+
  geom_count()
```
geom_count() that counts the number of observations at each location, then maps the count to point area. It's useful in discrete situations, but it doesn't work when points are overlapping but not in exactly same place.
geom_jitter() adds a small amount of random variation to the location of each point, and is a useful way of handling overplotting caused by discreteness in smaller datasets. 

### 4.
```{r 3.8.1.4}
ggplot(data = mpg, mapping = aes(x= cty, y= hwy, fill= cyl))+
  geom_boxplot()
ggplot(data = mpg, mapping = aes(x= cty, y= hwy, fill= cyl))+
  geom_boxplot(position = "dodge")
```
The default adjustment is position_ dodge. 

## 3.9.1 
### 2.
lab() changes labels on axes and legends. 

### 4. 

highway has better mpg than the city's. coord_fixed is important because we want to maintain the slope of the line. geom_abline add reference lines to a plot, either horizontal, vertical or diagonal specified by slope and intercept. 

## 4.4.1
### 1. 
the second my_var1able is misspelled with a "1" instead of "i"

### 2.
The corrected commands shall be as belowed 
```{r}
library(tidyverse)

ggplot(data = mpg)+
  geom_point(mapping = aes(x= displ, y= hwy))

filter(mpg, cyl == 8)
filter(diamonds, carat > 3)
```
## 5.2.4
### 1.1
```{r}
library(nycflights13)
filter(flights, arr_delay>=120)

###1.2

filter(flights, dest == 'IAH' | dest == 'HOU')

###1.3 

filter(flights, carrier %in% c('UA', 'AA', 'DL'))

###1.4

filter(flights, month >= 7 & month <= 9)

###1.5

filter(flights, arr_delay > 120, dep_delay <= 0)

###1.6

filter(flights, dep_delay >= 60, dep_delay-arr_delay > 30)

###1.7

filter(flights, dep_time <= 600 | dep_time == 2400)
```

###2 
between() is a shortcut for r x >= left & x <= right. It's another way of testing two inequalities at once. 
```{r}
filter(flights, between(month, 7, 9))
filter(flights, !between(dep_time, 601, 2359))

###3.
summary(flights)
#8255 flights have a missing dep_time, 8255 have a missing dep_delay, 8713 have a missing arr_time, 9430 have a missing arr_delay, and 9430 have a missing air_time.
```
###4.
NA^0 equal to 1 since any non-zero number to the power of 0 is 1. 
the | operator means or, so if either of the terms are true, the whole expression returns true since the right half returns true
In FALSE & NA, one of the terms is false, so the expression evaluates to FALSE.

###5.4.1.1
```{r}
select(flights, dep_time,  dep_delay, arr_time, arr_delay)
select(flights, c(dep_time,  dep_delay, arr_time, arr_delay))
flights %>% select(dep_time,  dep_delay, arr_time, arr_delay)
flights %>% select_("dep_time",  "dep_delay", "arr_time", "arr_delay")

###2

flights %>% select(dep_delay, dep_delay, dep_delay)
#nothing happens. 

###3
#It returns all the variables I ask for. 
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
flights %>% select(one_of(vars))

###4
#The default helper functions are insensitive to case.This can be changed by input ignore.case=FALSE. 
select(flights, contains("TIME"))
select(flights, contains("TIME", ignore.case = FALSE))
```








